Supplementary information

### 2016-12-20 Supplementary information.tex
Changes to new EVI calculation

C\'{o}rdoba&Caribbean&Cispat\'{a} bay-Ca\~{n}o Tij\'{io} 1&-75.8378&9.3566&147.50&\citet{Bolivar_inpreparation}\\ 
C\'{o}rdoba&Caribbean&Cispat\'{a} bay-Ca\~{n}o Tij\'{io} 2&-75.8284&9.3606&186.60&\citet{Bolivar_inpreparation}\\ 

>>>>

C\'{o}rdoba&Caribbean&Cispat\'{a} bay-Ca\~{n}o Tij\'{o} 1&-75.8378&9.3566&147.50&\citet{Bolivar_inpreparation}\\ 
C\'{o}rdoba&Caribbean&Cispat\'{a} bay-Ca\~{n}o Tij\'{o} 2&-75.8284&9.3606&186.60&\citet{Bolivar_inpreparation}\\ 
